Data Migration under a Changing Schema in Ampersand

### 2023-12-07 2022Migration/articleMigrationFoIKS.tex
typo

   Exhibit D: When the last atom of {tt A} is paired with an atom from {\tt B}, requirement~\ref{eqn:readyForMoC} is satisfied and the prototype informs the user to remove the migration system.

>>>>

   Exhibit D: When the last atom of {\tt A} is paired with an atom from {\tt B}, requirement~\ref{eqn:readyForMoC} is satisfied and the prototype informs the user to remove the migration system.
